\newpage
\addcontentsline{toc}{section}{Tài liệu tham khảo}
\renewcommand\refname{Tài liệu tham khảo}
\begin{thebibliography}{3}
    \item Deng J., Zhang S., and Ma J. (2023). Self-Attention-Based Deep Convolution LSTM Framework for Sensor-Based Badminton Activity Recognition. Sensors, 23(20), 8373. \href{https://doi.org/10.3390/s23208373}{Link tham khảo}
    \item Ordóñez F. and Roggen D. (2016). Deep convolutional and LSTM recurrent neural networks for multimodal wearable activity recognition. Sensors, 16(1), 115. \href{https://doi.org/10.3390/s16010115}{Link tham khảo}
    \item Vaswani A., Shazeer N., Parmar N., et al. (2017). Attention is all you need. arXiv.org, <https://arxiv.org/abs/1706.03762>. \href{https://arxiv.org/abs/1706.03762}{Link tham khảo}
    \item Deb S.D., Jha R.K., Kumar R., et al. (2023). CoVSeverity-Net: an efficient deep learning model for COVID-19 severity estimation from Chest X-Ray images. Research on Biomedical Engineering, 39(1). \href{https://doi.org/10.1007/s42662-022-00377-1}{Link tham khảo}
    \item Fu F., Chen J., Zhang J. và cộng sự. (2024). Are Synthetic Time-series Data Really not as Good as Real Data?. arXiv.org, <https://arxiv.org/abs/2402.00607>. \href{https://arxiv.org/abs/2402.00607}{Link tham khảo}
    \item Ioffe S. và Szegedy C. (2015). Batch normalization: Accelerating deep network training by reducing internal covariate shift. arXiv.org, <https://arxiv.org/abs/1502.03167>.
    \item (2022). (PDF) Integrating statistical and machine learning approaches to identify receptive field structure in neural populations. ResearchGate.
    \item Zheng Y., Liu Q., Chen E. và cộng sự. (2014). Time series classification using Multi-Channels Deep Convolutional neural networks. Lecture notes in computer science.
    \item 1.Faisal M.A.A. (2022). ASL-Sensor-Dataglove-Dataset.zip. , accessed: 07/12/2024.
    \item Yoon J., Jarrett D., và Van Der Schaar M. (2019). Time-series generative adversarial networks. Neural Information Processing Systems, 32.
    \item Bishop C. M. (1995). Neural Networks for Pattern Recognition, Nhà in Đại học Oxford. ISBN 0-19-853864-2
    \item Microchip Technology. (truy cập lần cuối tháng 12/2023). "ATmega328P Microcontroller." Truy cập từ: \href{https://www.microchip.com/en-us/product/ATmega328P}{Link tham khảo} 
    \item Arduino Kit Vietnam. (Ngày đăng 12/06/2023). "Hướng dẫn sử dụng cảm biến uốn cong (Flex Sensor) với Arduino." Truy cập từ: \href{https://arduinokit.vn/huong-dan-su-dung-cam-bien-uon-cong-flex-sensor-voi-arduino/}{Link tham khảo} 
    \item Pham, D. K. (Ngày đăng 22/04/2019). "Lý thuyết về mạng LSTM." Truy cập từ: \href{https://phamdinhkhanh.github.io/2019/04/22/Ly_thuyet_ve_mang_LSTM.html?fbclid=IwAR0rBn2SL1vPNYmLgixLra-BoMMb6f98mhPrMxv_BhX13_9sK3_4da1vN6c}{Link tham khảo}
    \item Brownlee, J. (Ngày đăng 28/08/2020). "How to Develop RNN Models for Human Activity Recognition (Time Series Classification)." Truy cập từ: \href{https://machinelearningmastery.com/how-to-develop-rnn-models-for-human-activity-recognition-time-series-classification/}{Link tham khảo}  
    
\end{thebibliography}